---
title: "EDA LA-1"
output:
  pdf_document: default
  word_document: default
  html_document:
    df_print: paged
date: '2022-06-23'
author:
  - MONISHA M, 1NT19IS085
  - ANANYA ANANTH, 1NT19IS021
  
---
### 1.Reading the data from the dataset
```{r}
data=read.csv("A:/3rd year BE/EDA/COVID-19 India Statewise Vaccine Data.csv")
```

### 2. import library ggplot2
```{r}
library(ggplot2)
```

### 3. Simple scatter plot 
```{r}
plot(data$Dose.1, data$Dose.2)
```


### 4.Simple Scatter plot using ggplot2
```{r}
library(ggplot2)
ggplot(data, aes(x = Dose.1, y = Dose.2)) +
 geom_point()
```

### 5.Scatter plot without passing a dataset
```{r}
ggplot(data = NULL, aes(x = mtcars$wt, y = mtcars$mpg)) +
 geom_point()
```

### 6.Simple line graph
```{r}
plot(data$Dose.1, data$Dose.2, type = "l")
```

### 7. To change column names
```{r}
library(dplyr)
data=rename(data,"state"=State.UTs)
data=rename(data,"dose1"=Dose.1)
data=rename(data,"dose2"=Dose.2)
data=rename(data,"total"=Total.Vaccination.Doses)
data=rename(data,"population"=Population)
data
```



### 8. Line and Point plot
```{r}
plot(data$dose1, data$dose2, type = "l")
points(data$dose1, data$dose2)
```

### 9.Line and Point plot with colours
```{r}
plot(data$dose1, data$dose2, type = "l")
points(data$dose1, data$dose2)
lines(data$dose1, data$dose2/2, col = "red")
points(data$dose1, data$dose2/2, col = "red")
```
### 10.Line graph using ggplot2   
```{r}
library(ggplot2)
ggplot(data, aes(x = dose1, y = dose2)) +
 geom_line()
```
### 11.Point and Line graph usinf ggplot2
```{r}
ggplot(data, aes(x = dose1, y = dose2))+
 geom_line() +
 geom_point()
```
### 12.Simple Bare plot 
```{r}
barplot(data$dose1)
```
### 13.Bar graph using ggplot2
```{r}
ggplot(data,aes(x=state,y=dose2))+geom_col()
```
### 14.Simple Histogram plot
```{r}
hist(data$total)
```
### 15.Simple histogram by specifying bins with breaks
```{r}
hist(data$dose1,breaks=100)
```
### 16.Histogram using ggplot2
```{r}
library(ggplot2)
ggplot(data,aes(x=dose1))+geom_histogram()
```
###17.Box plot using ggplot2
```{r}
data1=head(data)
plot(factor(data1$state),data1$total)
```
### 18.Box plot using ggplot2
```{r}
ggplot(data1,aes(x=state,y=total))+geom_boxplot()
```
### 19.Simple function curve
```{r}
curve(x^3+x+10,from=-4,to=4)
```
### 20.Plotting curve using user defined function
```{r}
myfun <- function(xvar) {
 1 / (1 + exp(-xvar + 10))
}
curve(myfun(x), from = 0, to = 20)
curve(1 - myfun(x), add = TRUE, col = "red")
```
### 21.Simple curve using ggplot2
```{r}
library(ggplot2)
# This sets the x range from 0 to 20
ggplot(data.frame(x = c(0, 20)), aes(x = x)) +
 stat_function(fun = myfun, geom = "line")
```
### 22.Bar graph using colour and fill colour
```{r}
ggplot(data,aes(x=state,y=total))+geom_col(fill="purple",colour="black")
```
### 23.Bar graph usig gruping bars together
```{r}
ggplot(data1,aes(x=state,y=total,fill=dose1))+geom_col(postion='dodge')
```
### 24.Simple Bar graph and adding colours using geom_col and fill region
```{r}
library(dplyr)

ggplot(data1,aes(x=state,y=dose1,fill=dose2))+
  geom_col()
```
### 25. Box plot suing colour fill and changing x label
```{r}
ggplot(data1, aes(x = reorder(dose1,dose2), y = total, fill = state)) +
 geom_col(colour = "black")+
 xlab("Satate")
```
### 26.Using position ="identity" in Bar graph 

position = "identity": This will prevent a warning message about stacking not being well defined for negative numbers

```{r}
ggplot(data1, aes(x = reorder(dose1,dose2), y = total, fill = state)) +
 geom_col(position = "identity")
```

### 27.Bar plot using scale_fill_manual() and remove the legend with guide = FALSE
We can change the colors with scale_fill_manual() and remove the legend with
guide = FALSE. We also addedx a thin black outline around
each of the bars by setting colour and specifying size, which is the thickness of the
outline (in millimeters)
```{r}
data2=data[c(7,9),]
ggplot(data2, aes(x = reorder(dose1,dose2), y = total, fill = state)) +
 geom_col(position = "identity", colour = "black", size = 0.25) +
 scale_fill_manual(values = c("#CCEEFF", "#FFDDDD"), guide = FALSE)
```
### 28. Grouped Bard graph with narrow bars

```{r}
data3=data[c(7,9,12,13,14),]
ggplot(data3, aes(x = state, y = total, fill = state)) +
 geom_col(width = 0.5, position = "dodge")
```
### 29.Grouped Bard graph with narrow bars with some space in between
```{r}
ggplot(data3, aes(x = state, y = total, fill = state)) +
 geom_col(width = 0.5, position = position_dodge(0.7))
```
### 30.Adding labels in Bar graph (labels under the bars)

```{r}
ggplot(data3, aes(x = interaction(dose1, dose2), y = population)) +
 geom_col() +
 geom_text(aes(label = population), vjust = 1.5, colour = "white")
```
### 31. Adding labels to bar graph (labels above bars)
```{r}
ggplot(data3, aes(x = interaction(dose1, dose2), y = population)) +
 geom_col() +
 geom_text(aes(label = population), vjust = -0.2)
```
### 32.Simple Cleveland dot plot
```{r}
ggplot(data, aes(x = population, y = state)) +
 geom_point()
```
### 33. To improve the appearamce of the above graph
```{r}
ggplot(data, aes(x = population, y = reorder(state, population))) +
 geom_point(size = 3) + # Use a larger dot
 theme_bw() +
 theme(
 panel.grid.major.x = element_blank(),
 panel.grid.minor.x = element_blank(),
 panel.grid.major.y = element_line(colour = "grey60", linetype = "dashed")
 )
```
### 34.To swap the axes in a Cleveland graph
```{r}
ggplot(data, aes(x = reorder(state, total), y = total)) +
 geom_point(size = 3) + # Use a larger dot
 theme_bw() +
 theme(
 panel.grid.major.y = element_blank(),
 panel.grid.minor.y = element_blank(),
 panel.grid.major.x = element_line(colour = "grey60", linetype = "dashed"),
 axis.text.x = element_text(angle = 60, hjust = 1)
 )
```
### 35.Simple Line graph using ggplot() and geo_line() 
```{r}
ggplot(data, aes(x = dose1, y = dose2)) +
 geom_line()
```
### 36.Line graph with the factor on x axis
```{r}
ggplot(data3, aes(x = factor(state), y = dose2, group = 1)) +
 geom_line()
```
### 37. Line graph with manually set y range
```{r}
ggplot(data, aes(x = dose1, y = dose2)) +
 geom_line() +
 ylim(0, max(data$state))
```


### 38.Another method to plot the above graph
```{r}
ggplot(data, aes(x = dose1, y = dose2)) +
 geom_line() +
 expand_limits(y = 0)
```
### 39. Adding poitns to a line graph
```{r}
ggplot(data, aes(x = dose1, y = dose2)) +
 geom_line() +
 geom_point()

```


### 40. Line graph with log on y axis
```{r}
ggplot(data, aes(x = dose1, y = dose2)) +
 geom_line() +
 geom_point() +
 scale_y_log10()
```
### 41. Line graph with variable mapped to colour
```{r}
ggplot(data3, aes(x = dose1, y = total, colour = dose2)) +
 geom_line()
```
### 42. Line graph with different shapes
```{r}
ggplot(data3, aes(x = dose1, y = dose2, shape = state)) +
 geom_line() +
 geom_point(size = 4) 
```
### 43. With coloured fill shapes in the above graph
```{r}
ggplot(data1, aes(x = dose1, y = dose2, fill = state)) +
 geom_line() +
 geom_point(size = 4, shape = 21) 
```
### 44.Line graph with different line type, line size and line colour
```{r}
ggplot(data, aes(x = dose1, y = population)) +
 geom_line(linetype = "dashed", size = 1, colour = "blue")
```
### 45. Line graph with changing the line colour and line size for better visual
```{r}
ggplot(data, aes(x = dose1, y = dose2)) +
 geom_line(colour = "darkgreen", size = 1.5)
```

### 46. Line graph with points and chganging the line type and point type
```{r}
ggplot(data3, aes(x = dose1, y = dose2)) +
 geom_line(linetype = "dashed") +
 geom_point(shape = 22, size = 3, fill = "red")
```
### 47. Line graph with other modifications outside aes() function
setting the size, shape, colour, and/or fill outside of aes() function
```{r}
ggplot(data3, aes(x = dose1, y = dose2)) +
 geom_line() +
 geom_point(size = 4, shape = 22, colour = "darkred", fill = "pink")
```
### 48.Line and point graph with a white fill and shape circle
```{r}
ggplot(data3, aes(x = dose1, y = dose2)) +
 geom_line() +
 geom_point(size = 4, shape = 21, fill = "white")
```
### 49. Line and Point graph using scale_colour_brewer and scale_colour_manual functions
 to use a different palette,using scale_colour_brewer() or scale_colour_manual()
```{r}
ggplot(data3, aes(x = dose1, y = dose2, fill = "pink")) +
 geom_line() +
 geom_point(shape = 21, size = 3) +
 scale_fill_manual(values = "white")
```
### 50. Simple Area plot using ggplot2
```{r}

ggplot(data, aes(x = dose1, y = dose2)) +
 geom_area()
```
### 51.Area plot with improvisation in visuals
```{r}
ggplot(data, aes(x = dose1, y = dose2)) +
 geom_area(colour = "black", fill = "blue", alpha = .2)
```
### 52. Plotting simple Ribbon graph 
```{r}
ggplot(data, aes(x = dose1, y = dose2)) +
geom_ribbon(aes(ymin = dose1 - dose2,
 ymax = dose1 + dose2),
 alpha = 0.2) +
geom_line()
```
### 53.Ribbon graph with upper and lower bounds as dotted lines
```{r}
ggplot(data, aes(x = total, y = population)) +
 geom_line(aes(y = total - population), colour = "grey50",
 linetype = "dotted") +
 geom_line(aes(y = total + population), colour = "grey50",
 linetype = "dotted") +
 geom_line()
```
### 54. Scatter plot using ggplot2
```{r}
ggplot(data[1:15,], aes(x = state, y = total)) +
 geom_point()
```

### 55. Scaotter plot with hollow circles
```{r}
ggplot(data, aes(x = dose1, y = dose2)) +
 geom_point(shape = 21)
```

### 56.Scatter plots with larger points
```{r}
ggplot(data, aes(x = dose1, y = dose2)) +
 geom_point(size = 3)
```

### 57.Grouping points by variables mapped to colour or shape
```{r}
ggplot(data3, aes(x = dose1, y = dose2, shape = state, colour = state)) +
 geom_point()
```
### 58.Scatter plot with scale_shape_manual and scale_colour_brewer functions
```{r}
ggplot(data2, aes(x = dose1, y = dose2, shape = state, colour = state)) +
 geom_point() +
 scale_shape_manual(values = c(1,2)) +
 scale_colour_brewer(palette = "Set1")
```
### 59.Scatter plot with different point shape
```{r}
ggplot(data, aes(x = dose1, y = dose2)) +
 geom_point(shape = 3)
```
### 60. Adding fitted regression model lines
```{r}
hw_sp <- ggplot(data, aes(x = dose1, y = dose2))
hw_sp +
 geom_point() +
 stat_smooth(method = lm)
```
### 61. The above plot with 99% confidence region
```{r}
hw_sp +
 geom_point() +
 stat_smooth(method = lm, level = 0.99)
```
### 62.Adding labels to the scatter plot
```{r}
countries_sp <- ggplot(data3, aes(x = dose1, y = dose2)) +
 geom_point()
countries_sp +
 geom_text(aes(label = state), size = 4)
```
### 63. Scatter plot with labels using geo_text() function
```{r}
library(ggrepel)
countries_sp +
 geom_text(aes(label = state), size = 3, vjust = 0)
```
### 64.Plotting 2 histograms using facet_gri() function
```{r}
ggplot(data2, aes(x = dose1)) +
 geom_histogram(fill = "white", colour = "black") +
 facet_grid(state ~ .)
```
### 65.Above histograms with modified aesthetics
```{r}
ggplot(data2, aes(x = population)) +
 geom_histogram(fill = "blue", colour = "black") +
 facet_grid(state ~ .)
```
### 66. Combining the stacked histograms as one hostogram for better comparison
 Map state to fill, make the bars NOT stacked, and make them semitransparent
```{r}
ggplot(data1, aes(x = dose1, fill = state)) +
 geom_histogram(position = "identity", alpha = 0.4)
```
### 67.Simple Density curve 
```{r}
ggplot(data, aes(x = total)) +
 geom_density()
```

### 69.Density curve using geom_line() function
```{r}
ggplot(faithful, aes(x = waiting)) +
 geom_line(stat = "density") +
 expand_limits(y = 0)
```
### 70.Plotting Density curve with different smoothness of curve 
```{r}
ggplot(data, aes(x = total)) +
 geom_line(stat = "density") +
 geom_line(stat = "density", adjust = .25, colour = "red") +
 geom_line(stat = "density", adjust = 2, colour = "blue")
```
### 71.Plotting Density curve with colour fill and alpha as 0.2
```{r}
ggplot(data, aes(x = total)) +
 geom_density(fill = "blue", alpha = .2) 
```
### 72.Plotting Density plot overlaid on a histogram
```{r}
ggplot(data, aes(x = dose1, y = ..density..)) +
 geom_histogram(fill = "cornsilk", colour = "grey60", size = .2) +
 geom_density() 
```
### 73.Frequency polygon with ggplot2
```{r}
ggplot(data, aes(x=total)) +
 geom_freqpoly()
```
### 74.Box plot using ggplot2
```{r}
data4=data[1,]
ggplot(data3, aes(x = factor(state), y = dose1/10000)) +
 geom_boxplot()
```
### 75.Simple Violin plot using ggplot2 
```{r}
hw_p <- ggplot(data, aes(x = dose1, y = dose2))
hw_p +
 geom_violin()
```
### 76. Box plot overlaid on Violin plot
```{r}
hw_p +
 geom_violin() +
 geom_boxplot(width = .1, fill = "red", outlier.colour = NA) +
 stat_summary(fun.y = median, geom = "point", fill = "white", shape = 21,
 size = 2.5)
```
### 77. Trimming the tails of violin plot
The default range goes from the minimum to maximum data values; the flat ends of
the violins are at the extremes of the data. It’s possible to keep the tails, by setting trim= FALSE
```{r}
hw_p +
 geom_violin(trim = FALSE)
```
### 78. Violin plot with scale="count" 
By default, the violins are scaled so that the total area of each one is the same (if trim
= TRUE, then it scales what the area would be including the tails). Instead of equal
areas, you can use scale = "count" to scale the areas proportionally to the number
of observations in each group 
```{r}
hw_p +
 geom_violin(scale = "count")
```
### 79.Simple Dot plot using ggplot2 
```{r}
c2009 <- data %>%
 filter(total<= 30381117 & total >= 1313783)
# Create a base ggplot object using `c2009`, called `c2009_p` (for c2009 plot)
c2009_p <- ggplot(c2009, aes(x = dose1))
c2009_p +
 geom_dotplot()
```

### 80.Plotting line graph on top of shaded regions
```{r}
ggplot(data, aes(x = dose1, y = dose2)) +
geom_ribbon(aes(ymin = dose2 - dose1,
ymax = dose1 + dose2),
alpha = 0.2) +
geom_line()
```


### 81.Area graph With a dotted line for upper and lower bounds
```{r}
ggplot(data, aes(x = dose1, y = dose2)) +
geom_line(aes(y = dose1 - dose2), colour = "grey50",
linetype = "dotted") +
geom_line(aes(y = dose1 + dose2), colour = "grey50",
linetype = "dotted") +
geom_line()
```

### 82.Plotting areaplot with colours for better analysis
```{r}
ggplot(data, aes(x = dose1, y = dose2)) +
 geom_area(colour = "black", fill = "blue", alpha = .2)
```

### 83.Plotting areaplot
```{r}
ggplot(data, aes(x = population, y = dose1)) +
 geom_area()
``` 

### 84.Plotting dashed lined raph with points
```{r}
ggplot(data, aes(x = dose1, y = dose2, colour = state)) +
 geom_line(linetype = "dashed") +
 geom_point(shape = 22, size = 3, fill = "white")
```

### 85.Plotting dashed line graph
```{r}
ggplot(data, aes(x = dose1, y = dose2)) +
 geom_line(linetype = "dashed", size = 1, colour = "blue")
```

### 86.Mapping variables to propertoes of a point of different colors and same shape
```{r}
ggplot(data, aes(x = dose1, y = dose2, fill = state)) +
 geom_line() +
 geom_point(size = 4, shape = 21)
```

### 87.Mapping variables to propertoes of a point
```{r}
ggplot(data, aes(x = dose1, y = dose2, shape = state)) +
 geom_line() +
 geom_point(size = 4)
```


### 89.Plotting line and point graph for ans data

```{r}
ggplot(data, aes(x = dose1, y = dose2)) +
 geom_line() +
 geom_point()
```
### 90.Plotting the line and point graph with inconsistent data points
```{r}
ggplot(data, aes(x = dose1, y = population)) +
 geom_line() +
 geom_point()
```
### 91.Plotting the line and point graph with inconsistent data points and log on y axis
```{r}
ggplot(data, aes(x = dose2, y = population)) +
 geom_line() +
 geom_point() +
 scale_y_log10()
```
### 92.Adding mapsup colour to line graph
```{r}
ggplot(data, aes(x = dose2, y = dose1, colour = population)) +
 geom_line()
```
### 93.Plotting Dendogram for cluster classification
```{r}
hc <- hclust(dist(datam))
# Make the dendrogram
plot(hc)
# With text aligned
plot(hc, hang = -1)
```
### 94.Correlation matrix with correlation coefcients
```{r}
col <- colorRampPalette(c("#BB4444", "#EE9988", "#FFFFFF", "#77AADD", "#4477AA"))
corrplot(mcor, method = "shade", shade.col = NA, tl.col = "black", tl.srt = 45,
 col = col(200), addCoef.col = "black", cl.pos = "n", order = "AOE")
```

### 95.Correlation matrix with coloured squares
```{r}
corrplot(mcor, method = "shade", shade.col = NA, tl.col = "black", tl.srt = 45)
```

### 96.Correlation matrix   
```{r}
library(corrplot)
datam=data.matrix(data3)
mcor <- cor(datam)
corrplot(mcor)
```

### 97.Points and density mapped to alpha
```{r}
faithful_p +
 geom_point() +
 stat_density2d(aes(alpha = ..density..), geom = "tile", contour = FALSE)
```

### 98.Density plot with smaller bandwidth in the x and y direction
```{r}
faithful_p +
 stat_density2d(aes(fill = ..density..), geom = "raster", contour = FALSE)
```

### 99.Above plot with Contour lines, with height mapped to color
```{r}
faithful_p +
 stat_density2d(aes(colour = ..level..))
```
### 100. Making a density plot of 2-dimentional data
```{r}
faithful_p <- ggplot(data, aes(x = dose1, y = dose2))
faithful_p +
 geom_point() +
 stat_density2d()
```


# Git Hub link to the codes: 
https://github.com/leoo07/Exploratory-Data-Analysis-R-commands
